\ttitle

### 2013-02-01 Chapters/Chapter2.tex
Explaining more

@@

>>>>

\subsection{Statistical methods}
An method to process data, or create a basis for further processing, is by 
analyzing the statistical properties of a data set. When there is a continuous 
stream of data, it is possible to extract events by comparing the statistical 
properties of sliding time windows. By definition, events have a different 
statistical profile then their background. When two consecutive actions are 
regarded as the background, then a transition is an event between them.

\subsection{Hidden Markov Models Based Methods}

\subsection{Bayesian Methods}

@@

\subsection{Hidden Markov Models}
Viterbi algorithm / path; find the most likely sequence of cause-states for 
the observed measures.
